### 2018-03-27 Paper/intro.tex
intro pass 1 complete

In the present work, we focus our efforts on uncertainty analysis in predictions of NEMD simulations
for phonon transport.  As discussed earlier, predictions from NEMD
exhibit large discrepancies with experimental observations depending upon system size and potentially
due to variability in the applied thermal gradient. Additionally, the thermal conductivity estimates are
tightly coupled with parameter values associated with the inter-atomic potential. Hence, we set out to
accomplish multiple objectives through this research effort: First, we construct response surfaces
in order to characterize the dependence of discrepancy in thermal conductivity estimates from NEMD
with the experimental data on system size and applied thermal gradient. Second, we perform
sensitivity analysis to study the impact of SW potential parameter values on variability in predictions.
Third, we exploit our findings from sensitivity analysis to discern parameters for calibration in a Bayesian
setting in order to enhance the predictability of NEMD simulations.

>>>>

In the present work, we focus our efforts on uncertainty analysis in predictions of NEMD simulations
for phonon transport using a silicon bar. An overview of the set-up for the simulations is
provided in Section~\ref{sec:setup}. As discussed earlier, predictions from NEMD
exhibit large discrepancies with experimental observations depending upon system size and potentially
due to variability in the applied thermal gradient. Additionally, the thermal conductivity estimates are
tightly coupled with parameter values associated with the inter-atomic potential. Hence, we set out to
accomplish multiple objectives through this research effort: First, we construct response surfaces
in order to characterize the dependence of discrepancy in thermal conductivity estimates (between
MD simulations and experiments) on system size, and applied thermal gradient~(Section~\ref{sec:response}).
Second, we perform sensitivity analysis to study the impact of SW potential parameter values on 
variability in predictions~(Section~\ref{sec:sense}).
Third, we exploit our findings from sensitivity analysis to discern important parameters and hence
reduce the dimensionality of the problem~(Section~\ref{sec:ros}). Fourth, we illustrate calibration
of the important parameters in a Bayesian setting to evaluate their posterior
distributions~(Section~\ref{sec:bayes}). Construction of the
response surfaces, parametric sensitivity analysis, and Bayesian calibration can all be computationally
challenging endeavors especially in situations involving compute-intensive simulations as in the
case of NEMD. We therefore employ polynomial choas (PC) surrogates~\cite{Xiu:2002,Ghanem:1990}
using non-intrusive spectral approaches~\cite{Olivier:2010} to reduce computational effort pertaining
to the aforementioned objectives. Moreover, since the construction of a PC surrogate itself can be
expensive, we demonstrate in Section~\ref{sec:sense}, a novel approach that implements derivative-based
sensitivity measures~\cite{Sobol:2010} to a priori reduce the dimensionality of the surrogate while
ensuring reasonable predictive accuracy.
